|

### 2023-03-08 paper.tex
edit author list and minor edits.

\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}

@@

@@

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex

@@

  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,

@@

\usepackage{longtable,booktabs}

@@

\usepackage{graphicx,grffile}

@@

@@

\title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
\date{First version: December 14, 2018\\
This version: June 23, 2021\\
~\\
Feedback? Errors?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
~\\
~\\
Tired of Latex?\\
Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our \href{https://osf.io/k8jhx/}{new template}! :-)}

\begin{document}
\maketitle
\begin{abstract}
\noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}. I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{github repo}).\vspace{.8cm}
\end{abstract}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Access}: Research is normally funded by taxpayers (researchers are also taxpayers). Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software. Importantly, researchers from developing countries are even more dependent on free access to knowledge (Kirsop and Chan \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
\item
  \textbf{Reproducability}: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months. A fully reproducible setup will help you to trace back your own steps. Obviously, the same is true for other researchers who may want to understand your work and built on it. It may sound like a joke but why not aim for a document that can be used to reproduce your findings in 500 years.
\item
  \textbf{Errors}: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to \textbf{automatize} such steps and/or avoid them.
\item
  \textbf{Revisions}: Revising a paper takes much less time if you have all the code you need in one place, i.e., one \texttt{.rmd} file. For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.
\end{itemize}

@@

I assume that you are using R on a day-to-day basis. You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown. If you don't know what R Markdown is watch \href{https://vimeo.com/178485416}{this short video}. Then\ldots{}

\begin{itemize}
\tightlist
\item
  \ldots install \href{https://www.r-project.org/}{R} and \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (R Core Team \protect\hyperlink{ref-R2017}{2017}; RStudio Team \protect\hyperlink{ref-Rstudio2015}{2015}).
\item
  \ldots install \href{https://yihui.name/tinytex/}{tinytex}, a lightweight version of Tex Live (Allaire et al. \protect\hyperlink{ref-markdown2017}{2017}; Xie \protect\hyperlink{ref-tinytex}{2018}\protect\hyperlink{ref-tinytex}{b}).
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{'tinytex'}\NormalTok{, }\StringTok{'rmarkdown'}\NormalTok{))}
\NormalTok{tinytex}\OperatorTok{::}\KeywordTok{install_tinytex}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  \ldots install the packages below using the code below (Sievert et al. \protect\hyperlink{ref-plotly}{2017}; Xie \protect\hyperlink{ref-knitr3}{2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018}\protect\hyperlink{ref-knitr1}{a}; Zhu \protect\hyperlink{ref-kableextra}{2017}).
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
                   \StringTok{"stargazer"}\NormalTok{, }\StringTok{"plotly"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{,}
                   \StringTok{"bookdown"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\item
  \ldots download the 5 input files I created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}. Ignore the other files.
\item
  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

@@

  \begin{itemize}
  \tightlist
  \item
    I use paperpile to manage my references and export the \texttt{.bib} file into the folder that contains my \texttt{.rmd} file.
  \end{itemize}
\item
  \ldots a \texttt{data.csv} file (some raw data).
\item
  \ldots{} a \texttt{american-sociological-association.csl} file that defines the style of your bibliography.\footnote{You can download various citation style files from this webpage: \url{https://github.com/citation-style-language/styles}.}
\end{itemize}

@@

To see how referencing works simply see the different examples for figures, tables and sections below. For instance in Section \ref{sec:tables} you can find different ways of referencing tables. The code of the underlying \texttt{paper.rmd} will show you how I referenced Section \ref{sec:tables} right here namely with `\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.

@@

I would recommend to use the command below and simply add it to the appendix as I did here in Appendix \ref{sec:rsessioninfo}. This will make sure you always provide the package versions that you used in the last compilation of your paper. For more advanced tools see \href{https://rstudio.github.io/packrat/}{packrat}.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{cat}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"#"}\NormalTok{, }\KeywordTok{capture.output}\NormalTok{(}\KeywordTok{sessionInfo}\NormalTok{()), }\StringTok{"}\CharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\DataTypeTok{collapse =}\StringTok{""}\NormalTok{)) }
  \CommentTok{# or use message() instead of cat()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data <-}\StringTok{ }\KeywordTok{read.csv}\NormalTok{(}\StringTok{"data.csv"}\NormalTok{)}
\KeywordTok{head}\NormalTok{(data)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{dput}\NormalTok{(data)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data <-}\StringTok{ }\KeywordTok{structure}\NormalTok{(}\KeywordTok{list}\NormalTok{(}\DataTypeTok{X =} \DecValTok{1}\OperatorTok{:}\DecValTok{50}\NormalTok{, }\DataTypeTok{speed =} \KeywordTok{c}\NormalTok{(4L, 4L, 7L, 7L, 8L, 9L, 10L, }
\NormalTok{10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, }
\NormalTok{14L, 14L, 14L, 15L, 15L, 15L, 16L, 16L, 17L, 17L, 17L, 18L, 18L, }
\NormalTok{18L, 18L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 20L, 22L, 23L, 24L, }
\NormalTok{24L, 24L, 24L, 25L), }\DataTypeTok{dist =} \KeywordTok{c}\NormalTok{(2L, 10L, 4L, 22L, 16L, 10L, 18L, }
\NormalTok{26L, 34L, 17L, 28L, 14L, 20L, 24L, 28L, 26L, 34L, 34L, 46L, 26L, }
\NormalTok{36L, 60L, 80L, 20L, 26L, 54L, 32L, 40L, 32L, 40L, 50L, 42L, 56L, }
\NormalTok{76L, 84L, 36L, 46L, 68L, 32L, 48L, 52L, 56L, 64L, 66L, 54L, 70L, }
\NormalTok{92L, 93L, 120L, 85L)), }
\DataTypeTok{class =} \StringTok{"data.frame"}\NormalTok{, }\DataTypeTok{row.names =} \KeywordTok{c}\NormalTok{(}\OtherTok{NA}\NormalTok{, }
\OperatorTok{-}\NormalTok{50L))}
\end{Highlighting}
\end{Shaded}

@@

Table \ref{tab1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.} I normally use \texttt{stargazer()} (Hlavac \protect\hyperlink{ref-hlavac2013stargazer}{2013}) which offers extreme flexibility regarding table output (see \texttt{?stargazer}).

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(stargazer)}
\KeywordTok{stargazer}\NormalTok{(cars, }
          \DataTypeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab1"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H] \centering 
  \caption{Summary table with stargazer} 
  \label{tab1} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
speed & 50 & 15.400 & 5.288 & 4 & 12 & 19 & 25 \\ 
dist & 50 & 42.980 & 25.769 & 2 & 26 & 56 & 120 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(stargazer)}
\NormalTok{model1 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model3 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(dist }\OperatorTok{~}\StringTok{ }\NormalTok{speed, }\DataTypeTok{data =}\NormalTok{ cars)}
\KeywordTok{stargazer}\NormalTok{(model1, model2, model3,}
          \DataTypeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab2"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
          \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(cars}\OperatorTok{$}\NormalTok{speed, cars}\OperatorTok{$}\NormalTok{dist)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{mtcars}\OperatorTok{$}\NormalTok{cyl <-}\StringTok{ }\KeywordTok{as.factor}\NormalTok{(mtcars}\OperatorTok{$}\NormalTok{cyl) }\CommentTok{# Convert cyl to factor}
\KeywordTok{library}\NormalTok{(ggplot2)}
\KeywordTok{ggplot}\NormalTok{(mtcars, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x=}\NormalTok{wt, }\DataTypeTok{y=}\NormalTok{mpg, }\DataTypeTok{shape=}\NormalTok{cyl)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\DataTypeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
       \DataTypeTok{shape=}\StringTok{"Number of }\CharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{theme_classic}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

Every researcher has his own optimized setup. Currently I would recommend the following:

@@

  \begin{itemize}
  \tightlist
  \item
    Main file with text/code: ``paper.rmd'', ``report.rmd''
  \item
    Data files: "data\_xxxxxx.*"
  \item
    Image files: "fig\_xxxxxx.*"
  \item
    Tables files: "table\_xxxx.*"
  \item
    etc.
  \item
    Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called \texttt{fig\_1\_xxxxx.pdf}.
  \end{itemize}
\item
  Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
\item
  Name rchunks according to what they do or produce:

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-markdown2017}{}%
Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{Markdown: 'Markdown' Rendering for R}.

\leavevmode\hypertarget{ref-hlavac2013stargazer}{}%
Hlavac, Marek. 2013. ``Stargazer: LaTeX Code and Ascii Text for Well-Formatted Regression and Summary Statistics Tables.'' \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.

\leavevmode\hypertarget{ref-Kirsop2005-ro}{}%
Kirsop, Barbara and Leslie Chan. 2005. ``Transforming Access to Research Literature for Developing Countries.'' \emph{Serials Review} 31(4):246--55.

\leavevmode\hypertarget{ref-R2017}{}%
R Core Team. 2017. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing.

>>>>

\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}

@@

\usepackage{amsmath,amssymb}

@@

\usepackage{iftex}
\ifPDFTeX

@@

@@

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths

@@

\usepackage{graphicx}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
  pdfauthor={Paul Bauer, Mannheim Centre for European Social Research; Camille Landesvatter, Mannheim Centre for European Social Research},
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},

\title{\hfill\break
\hfill\break
\vspace{1cm}Writing a reproducible paper\\
in R Markdown\footnote{Corresponding address: \href{mailto:mail@paulcbauer.de}{\nolinkurl{mail@paulcbauer.de}}. Acknowledgments: We are grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul Bauer, Mannheim Centre for European Social Research \and Camille Landesvatter, Mannheim Centre for European Social Research}
\date{\hfill\break
First version: December 14, 2018\\
This version: March 08, 2023\\
Download: \url{https://osf.io/q395s}\\
\strut \\
Feedback? Errors? \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\
\href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{Github repository}\\
\strut \\
Tired of Latex?\\
Try \href{https://github.com/rstudio/pagedown}{Pagedown} with our \href{https://osf.io/k8jhx/}{new template}! :-)}

\begin{document}
\maketitle
\begin{abstract}
\noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below we outline some of the ``tricks''/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be downloaded \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{here}. We think we got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). We intend to update this file when we discover more convenient code (you can follow any updates through the corresponding \href{https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/}{github repo}).\vspace{.8cm}
\end{abstract}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Access}: Research is normally funded by taxpayers (researchers are also taxpayers). Hence, it should be freely accessible to everyone without any barriers, e.g., without requiring commercial software. Importantly, researchers from developing countries are even more dependent on free access to knowledge (\protect\hyperlink{ref-Kirsop2005-ro}{Kirsop and Chan 2005}).
\item
  \textbf{Reproducability}: Even if you have written a study and analyzed the data yourself you will forget what you did after a few months. A fully reproducible setup will help you to trace back your own steps. Obviously, the same is true for other researchers who may want to understand your work and built on it. It may sound like a joke but why not aim for a document that can be used to reproduce your findings in 500 years.
\item
  \textbf{Errors}: Manual steps in data analysis (e.g., manually copy/pasting values into a table etc.) may introduce errors. R Markdown allows you to \textbf{automatize} such steps and/or avoid them.
\item
  \textbf{Revisions}: Revising a paper takes much less time if you have all the code you need in one place, i.e., one \texttt{.rmd} file. For instance, if you decide to exclude a subset of your data you simply need to insert one line of your code at the beginning and everything is rebuilt/re-estimated automatically.
\end{itemize}

@@

We assume that you are using R on a day-to-day basis. You may have even started to work a little in R Markdown but you don't write your complete paper in R Markdown. If you don't know what R Markdown is watch \href{https://vimeo.com/178485416}{this short video}. Then\ldots{}

\begin{itemize}
\tightlist
\item
  \ldots install \href{https://www.r-project.org/}{R} and \href{https://www.rstudio.com/}{Rstudio} (most recent versions) (\protect\hyperlink{ref-R2017}{R Core Team 2017}; \protect\hyperlink{ref-Rstudio2015}{RStudio Team 2015}).
\item
  \ldots install \href{https://yihui.name/tinytex/}{tinytex}, a lightweight version of Tex Live (\protect\hyperlink{ref-markdown2017}{Allaire et al. 2017}; \protect\hyperlink{ref-tinytex}{Xie 2018b}).
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{install.packages}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{\textquotesingle{}tinytex\textquotesingle{}}\NormalTok{, }\StringTok{\textquotesingle{}rmarkdown\textquotesingle{}}\NormalTok{))}
\NormalTok{tinytex}\SpecialCharTok{::}\FunctionTok{install\_tinytex}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  \ldots install the packages below using the code below (\protect\hyperlink{ref-plotly}{Sievert et al. 2017}; \protect\hyperlink{ref-knitr3}{Xie 2014}, \protect\hyperlink{ref-knitr2}{2015}, \protect\hyperlink{ref-bookdown2}{2016}, \protect\hyperlink{ref-bookdown1}{2017}, \protect\hyperlink{ref-knitr1}{2018a}; \protect\hyperlink{ref-kableextra}{Zhu 2017}).
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{install.packages}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\StringTok{"rmarkdown"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{, }\StringTok{"kableExtra"}\NormalTok{,}
                   \StringTok{"stargazer"}\NormalTok{, }\StringTok{"plotly"}\NormalTok{, }\StringTok{"knitr"}\NormalTok{,}
                   \StringTok{"bookdown"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\item
  \ldots download the 5 input files we created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}. Ignore the other files.
\item
  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

@@

  \begin{itemize}
  \tightlist
  \item
    We use paperpile to manage my references and export the \texttt{.bib} file into the folder that contains my \texttt{.rmd} file.
  \end{itemize}
\item
  \ldots a \texttt{data.csv} file (some raw data).
\item
  \ldots{} a \texttt{american-sociological-association.csl} file that defines the style of your bibliography.\footnote{You can download various citation style files from this webpage: \url{https://github.com/citation-style-language/styles}.}
\end{itemize}

@@

To see how referencing works simply see the different examples for figures, tables and sections below. For instance in Section \ref{sec:tables} you can find different ways of referencing tables. The code of the underlying \texttt{paper.rmd} will show you how we referenced Section \ref{sec:tables} right here namely with `\texttt{Section\ \textbackslash{}@ref(sec:tables)}'.

@@

We would recommend to use the command below and simply add it to the appendix as we did here in Appendix \ref{sec:rsessioninfo}. This will make sure you always provide the package versions that you used in the last compilation of your paper. For more advanced tools see \href{https://rstudio.github.io/packrat/}{packrat}.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{cat}\NormalTok{(}\FunctionTok{paste}\NormalTok{(}\StringTok{"\#"}\NormalTok{, }\FunctionTok{capture.output}\NormalTok{(}\FunctionTok{sessionInfo}\NormalTok{()), }\StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{, }\AttributeTok{collapse =}\StringTok{""}\NormalTok{)) }
  \CommentTok{\# or use message() instead of cat()}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{read.csv}\NormalTok{(}\StringTok{"data.csv"}\NormalTok{)}
\FunctionTok{head}\NormalTok{(data)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{dput}\NormalTok{(data)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{structure}\NormalTok{(}\FunctionTok{list}\NormalTok{(}\AttributeTok{X =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{50}\NormalTok{, }\AttributeTok{speed =} \FunctionTok{c}\NormalTok{(4L, 4L, 7L, 7L, 8L, 9L, 10L, }
\NormalTok{10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, }
\NormalTok{14L, 14L, 14L, 15L, 15L, 15L, 16L, 16L, 17L, 17L, 17L, 18L, 18L, }
\NormalTok{18L, 18L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 20L, 22L, 23L, 24L, }
\NormalTok{24L, 24L, 24L, 25L), }\AttributeTok{dist =} \FunctionTok{c}\NormalTok{(2L, 10L, 4L, 22L, 16L, 10L, 18L, }
\NormalTok{26L, 34L, 17L, 28L, 14L, 20L, 24L, 28L, 26L, 34L, 34L, 46L, 26L, }
\NormalTok{36L, 60L, 80L, 20L, 26L, 54L, 32L, 40L, 32L, 40L, 50L, 42L, 56L, }
\NormalTok{76L, 84L, 36L, 46L, 68L, 32L, 48L, 52L, 56L, 64L, 66L, 54L, 70L, }
\NormalTok{92L, 93L, 120L, 85L)), }
\AttributeTok{class =} \StringTok{"data.frame"}\NormalTok{, }\AttributeTok{row.names =} \FunctionTok{c}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }
\SpecialCharTok{{-}}\NormalTok{50L))}
\end{Highlighting}
\end{Shaded}

@@

Table \ref{tab1} shows summary stats of your data.\footnote{To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.} We normally use \texttt{stargazer()} (\protect\hyperlink{ref-hlavac2013stargazer}{Hlavac 2013}) which offers extreme flexibility regarding table output (see \texttt{?stargazer}).

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(stargazer)}
\FunctionTok{stargazer}\NormalTok{(cars, }
          \AttributeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
          \AttributeTok{label=}\StringTok{"tab1"}\NormalTok{, }
          \AttributeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \AttributeTok{header=}\ConstantTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H] \centering 
  \caption{Summary table with stargazer} 
  \label{tab1} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
speed & 50 & 15.400 & 5.288 & 4 & 25 \\ 
dist & 50 & 42.980 & 25.769 & 2 & 120 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(stargazer)}
\NormalTok{model1 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(speed }\SpecialCharTok{\textasciitilde{}}\NormalTok{ dist, }\AttributeTok{data =}\NormalTok{ cars)}
\NormalTok{model2 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(speed }\SpecialCharTok{\textasciitilde{}}\NormalTok{ dist, }\AttributeTok{data =}\NormalTok{ cars)}
\NormalTok{model3 }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(dist }\SpecialCharTok{\textasciitilde{}}\NormalTok{ speed, }\AttributeTok{data =}\NormalTok{ cars)}
\FunctionTok{stargazer}\NormalTok{(model1, model2, model3,}
          \AttributeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
          \AttributeTok{label=}\StringTok{"tab2"}\NormalTok{, }
          \AttributeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \AttributeTok{column.labels =} \FunctionTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
          \AttributeTok{model.numbers =} \ConstantTok{FALSE}\NormalTok{,}
          \AttributeTok{header=}\ConstantTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plot}\NormalTok{(cars}\SpecialCharTok{$}\NormalTok{speed, cars}\SpecialCharTok{$}\NormalTok{dist)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{mtcars}\SpecialCharTok{$}\NormalTok{cyl }\OtherTok{\textless{}{-}} \FunctionTok{as.factor}\NormalTok{(mtcars}\SpecialCharTok{$}\NormalTok{cyl) }\CommentTok{\# Convert cyl to factor}
\FunctionTok{library}\NormalTok{(ggplot2)}
\FunctionTok{ggplot}\NormalTok{(mtcars, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{wt, }\AttributeTok{y=}\NormalTok{mpg, }\AttributeTok{shape=}\NormalTok{cyl)) }\SpecialCharTok{+} \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x=}\StringTok{"Weight (lb/1000)"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Miles/(US) gallon"}\NormalTok{, }
       \AttributeTok{shape=}\StringTok{"Number of }\SpecialCharTok{\textbackslash{}n}\StringTok{ Cylinders"}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{theme\_classic}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

Every researcher has his own optimized setup. Currently we would recommend the following:

@@

  \begin{itemize}
  \tightlist
  \item
    Main file with text/code: ``paper.rmd'', ``report.rmd''
  \item
    Data files: ``data\_xxxxxx.*''
  \item
    Image files: ``fig\_xxxxxx.*''
  \item
    Tables files: ``table\_xxxx.*''
  \item
    etc.
  \item
    Ideally, your filenames will correspond to the names in the paper. For instance, Figure 1 in the paper may have a corresponding file called \texttt{fig\_1\_xxxxx.pdf}.
  \end{itemize}
\item
  Use the document outline in R studio (Ctrl + Shift + O) when you work with R Markdown.
\item
  Name rchunks according to what they do or produce:

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-markdown2017}{}}%
Allaire, JJ, Jeffrey Horner, Vicent Marti, and Natacha Porte. 2017. \emph{\href{https://CRAN.R-project.org/package=markdown}{Markdown: 'Markdown' Rendering for r}}.

\leavevmode\vadjust pre{\hypertarget{ref-hlavac2013stargazer}{}}%
Hlavac, Marek. 2013. {``Stargazer: LaTeX Code and ASCII Text for Well-Formatted Regression and Summary Statistics Tables.''} \emph{URL: Http://CRAN. R-Project. Org/Package= Stargazer}.

\leavevmode\vadjust pre{\hypertarget{ref-Kirsop2005-ro}{}}%
Kirsop, Barbara and Leslie Chan. 2005. {``Transforming Access to Research Literature for Developing Countries.''} \emph{Serials Review} 31(4):246--55.

\leavevmode\vadjust pre{\hypertarget{ref-R2017}{}}%
R Core Team. 2017. \emph{\href{https://www.R-project.org/}{R: A Language and Environment for Statistical Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
